---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.

```{r}
tabgroupinfected<- xtabs(~infected+group,data=Genvoyabub)
tabgroupinfected
```
  The groups infected with Aids, 101 of them took Genvoyabub and 110 of them took the placebo.The groups not infected with Aids, 2361 of them took Genvoyabub and 2352 of them took the placebo.


```{r}
barchartGC(tabgroupinfected, type= "percent")
```

  It appears that there isn't much of a problem because people who have aids and took the drug and the people who have aids and took the placebo have a 50/50 scale this doesn't shows a difference.This means that th people who have aids are still going to have aids the drug or placebo didn't help them  It also appears that people who have no disease that took the placebo and the people that took the drug have about the same scale so there isn't much of a difference.



```{r}
chisqtestGC(tabgroupinfected)
```
   The p value is 0.5735. Given the condition of the null hypothesis if the null hypothesis is true then it would happen the probability of 57.35 percent of the time. This situation resulted in us failing to reject the null hypothesis because of the condition of it being higher than .05.





```{r}
GenvoyabubF <- filter(Genvoyabub,sex == "F")
tabgroupinfectedF<-xtabs(~infected+group,data=GenvoyabubF)
tabgroupinfectedF
```

  The female groups infected with Aids, 54 of them took Genvoyabub and 62 of them took the placebo.The groups not infected with Aids, 1177 of them took Genvoyabub and 1169 of them took the placebo.


```{r}
barchartGC(tabgroupinfectedF, type= "percent")
```

 It appears that there is problem because people who have aids and took the drug and the people who have aids and took the placebo don't have a 50/50 scale this shows a difference. This means that both the people that took the drug and the people that took the placebo both have a severe chance of having severe aids. It also appears that people who have no disease that took the placebo and the people that took the drug have about the same scale so there isn't much of a difference.

```{r}
chisqtestGC(tabgroupinfectedF)
```

  The p value is 0.5055. Given the condition of the null hypothesis if the null hypothesis is true then it would happen the probability of 50.55 percent of the time. This situation resulted in us failing to reject the null hypothesis because of the condition of it being higher than .05.

```{r}
GenvoyabubM <- filter(Genvoyabub,sex == "M")
tabgroupinfectedM<-xtabs(~infected+group,data=GenvoyabubM)
tabgroupinfectedM
```

 The male groups infected with Aids, 47 of them took Genvoyabub and 48 of them took the placebo.The groups not infected with Aids, 1184 of them took Genvoyabub and 1183 of them took the placebo.


```{r}
barchartGC(tabgroupinfectedM, type= "percent")
```
 
   It appears that there is problem because people who have aids and took the drug and the people who have aids and took the placebo don't have a 50/50 scale this shows a difference. This means that both the people that took the drug and the people that took the placebo both have a severe chance of having severe aids. It also appears that people who have no disease that took the placebo and the people that took the drug have about the same scale so there isn't much of a difference.
```{r}
chisqtestGC(tabgroupinfectedM)
```

   The p value is 1. Given the condition of the null hypothesis if the null hypothesis is true then it would happen the probability of 1 percent of the time. This situation resulted in us failing to reject the null hypothesis because of the condition of it being higher than .05.


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.



# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






