---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.

```{r}
Atripla <- xtabs (~infected +group, data=Atriplavast) 
Atripla
```
The groups infeccted with Aids, 103 of them took Atriplavast and 131 of them took the placebo.

```{r}
barchartGC (Atripla, type="percent")
```

It appears that there is problem because people who have aids and took the drug and the people who have aids and took the placebo don't havee a 50/50 scale this shows a difference. It also appears that people who have no disease that took the placebo and the people that took the drug have about the same scale so there isn't much of a difference.

```{r}
chisqtestGC(Atripla)
```

The p value is 0.0699. Given the condition of the null hypothesis if the null hypothesis is true then it would happen the probability of 3.2 percent of the time. This situation resulted in us failing to reject the null hypothesis because of the condition of it being higher than .05.



Female Atriplavast





# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






